CannonRV: Measuring radial velocities with a data-driven spectral model

### 2016-11-26 paper/ms.tex
Add validity of the normalization

To check whether it works, we can infer labels by using these normalized visit. If the inferred labels from each visit are similar, the normalization works. 
The details are in experiment 5.

@@

\centerline{Fig.11 Comparison of the calibrated spectrum and the data spectrum}
\bigskip

After that, we want to calibrate the spectrum for each visit. Choose the first star in figure 11 and normalize all visits for it. Then, plot them in figure 12. To check whether our normalization works, infer labels for each visit and compare them. If our normalization works, the inferred labels of each visit should be similar to each other.

@@

\centerline{Fig.12 Comparison of each visit for star XXR}
\bigskip

We also plot the histogram which shows the deviations of the inferred labels for each visits from the ones for combined spectrum. The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum. The data we use is the 614 stars in experiment 1 to 4. If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.

@@

\centerline{Fig.13 Histogram for the deviations of the inferred labels}
\bigskip

plot the correct radial velocity spetrum by using sinc interpolation
plot the inferred labels plot the normalized spectrum for each apvisit and compare
plot histogram of the deviation for inf labels for each visits.

@@

Comparison of the spectrum if we set the parameters shown in old figure 8. In old figure 8, the red line and the green line are on the top of each other
 \bigskip

\includegraphics[width=170mm]{d_figure_2.png}
\bigskip

\centerline{Diagnostic Fig.2 Comparison of the spectrum if we set the parameters shown in old figure 8}
\bigskip

 Comparison of the spectrum if we set the parameters shown in old figure 9. In old figure 9, the difference between red line and the green line is too big if we consider their parameters.
 \bigskip

\includegraphics[width=170mm]{d_figure_3.png}
\bigskip

\centerline{Diagnostic Fig.3 Comparison of the spectrum if we set the parameters shown in old figure 9}
\bigskip

 If we want a plot like old figure 9, we can manually set a=0.5, b=1 and c= -0.5. Here a+b+c is not equal to 1 and this is the cause of the offset.
 \bigskip

\includegraphics[width=170mm]{d_figure_4.png}
\bigskip

\centerline{Diagnostic Fig.4 Comparison of the spectrum if we want a big difference between the red line and the green line}
\bigskip

In diagnostic plot 5, I use four fake stars. The data spectra of these four stars are generated by moving their inferred spectra one pixel left. If my new code is right, a, b and c will be [1,0,0]. In diagnostic figure 5, a=1, b=0 and c=0.
\bigskip

\includegraphics[width=170mm]{d_figure_5.png}
\bigskip

\centerline{Diagnostic Fig.5 Comparison of the spectrum for the four fake stars}
\bigskip

>>>>

To check whether it works, we can infer labels by using these normalized visit. If the inferred labels from each visit are similar, the normalization works. The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum and we define them as $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H.

\begin{equation}
\triangle Teff = Teff_{inf}^{vs} - Teff_{inf}^{cb}
\end{equation}

$Teff_{inf}^{vs}$ and $Teff_{inf}^{cb}$ are the inferred labels for each visit and the combined spectrum.

If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works. The details are in experiment 5.

@@

\centerline{Fig.11 Comparison of the calibrated spectrum and the data spectrum for the four stars with biggest a-c}

\centerline{ The black line is the data spectrum. The green line is the inferred spectrum and the red line is the calibrated data spectrum}
\bigskip

We do the same thing four the four stars with biggest c-a.

@@

\centerline{Fig.12 Comparison of the calibrated spectrum and the data spectrum for the four stars with biggest c-a.}

\centerline{ The black line is the data spectrum. The green line is the inferred spectrum and the red line is the calibrated data spectrum}
\bigskip

After that, we want to calibrate the spectrum for each visit. To begin with, we need to check whether our normalization works. The method is to infer labels for each visit and compare them. If our normalization works, the inferred labels from each visit for the same star should be similar to each other. We plot the histogram which shows the deviations of the inferred labels of each visits from the ones of combined spectrum for the same star. The deviations for each star are defined as the inferred labels for every visit minus the ones from the combined spectrum and we define them as $\triangle Teff$, $\triangle$ logg and $\triangle$ Fe/H. The data we use is the 614 stars in experiment 1 to 4. If most of the deviations are small, the normalized spectrum for each visit doesn't lose shape, which means our normalization method works.

@@

\centerline{Fig.13 Histogram for Delta Teff}
\bigskip

\includegraphics[width=170mm]{figure_14.png}
\bigskip

\centerline{Fig.14 Histogram for Delta logg}

\includegraphics[width=170mm]{figure_15.png}
\bigskip

\centerline{Fig.15 Histogram for Delta Fe/H}
\bigskip

We can see that most of the deviations are close to 0, which means our normalization for each visit doesn't make the spectrum distort.

@@
